### 2024-09-26 manuscript.tex
Various improvements

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, RSV \emph{Aurora Australis} datasets provided by the
Australian Antarctic Program and the University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and the UC, RV \emph{Nathaniel B. Palmer} dataset provided
by the National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and the UC, HMNZS
\emph{Wellington} dataset provided by the Royal New Zealand Navy and the UC and
the Macquarie Island station dataset provided by the Atmospheric Radiation
Measurement and the UC.  We thank the scientific staff, the crew, and everyone
involved in collecting data on the voyages and stations, especially Kelly
Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and
Alex Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
provided by the Copernicus Climate Change Service and MERRA-2 provided by the
Global Modeling and Assimilation Office. We would like to dedicate this study
to the memory of Mike J. Harvey, who very substantially contributed to
obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
this study.

@@

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
Levante cluster of the DKRZ
(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
\url{https://luv.dkrz.de/register/}. The CERES products are available from the
project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The other
voyage and station data are openly available on Zenodo (). Subsetted model and
reanalysis data for the voyage tracks and the station and data processed with
the ALCF are openly available on Zenodo ().

>>>>

Cloud in some of the voyage and station data were previsouly analysed by other
authors. \cite{pei2023} compared the Macquarie Ib

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, AA15-16 dataset provided by the
Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and UC, RV \emph{Nathaniel B. Palmer} dataset provided
by the National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, HMNZS \emph{Wellington}
dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset was
provided by the Atmospheric Radiation Measurement (ARM). The MICRE dataset was
provided by ARM, the Australian Bureau of Meteorology, AAD and UC.  We thank
the scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
Harvey (†), Simon P.  Alexander and Alex Schuddeboom. We acknowledge the ICON
model output provided by the nextGEMS project and the Deutsches
Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the Copernicus
Climate Change Service and MERRA-2 provided by the Global Modeling and
Assimilation Office. We dedicate this study to the memory of Mike J. Harvey,
who very substantially contributed to obtaining atmospheric measurments on the
RV \emph{Tangaroa} voyages used in this study.

@@

The RV \emph{Polarstern} datasets are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
data are openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
Levante cluster of the DKRZ
(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
\url{https://luv.dkrz.de/register/}. The CERES products are available from the
project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
The TAN1802 data ara available on Zenodo
(\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
data are openly available on Zenodo (). Subsetted model and reanalysis data for
the voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().

\section*{Author contributions}

TODO
